High-order cognition is supported by complex but compressible brain activity patterns

### 2023-02-20 paper/main.tex
starting on intro, additional file reorganization
typo fixes

\author{Lucy L. W. Owen$^1, 2$, and Jeremy R. Manning\textsuperscript{$1,
*$}\\$^1$Department of Psychological and Brain Sciences,\\Dartmouth College,
Hanover, NH\\[0.1cm]$^2$Carney Institute for Brain Sciences,\\Brown University,
Providence, RI\\[0.1cm] \textsuperscript{*}Address correspondence to
jeremy.r.manning@dartmouth.edu}

@@

\bibliographystyle{apacite}
\bibliography{cdl.bib}

>>>>

\author{Lucy L. W. Owen\textsuperscript{1, 2}, and Jeremy R. Manning\textsuperscript{1,
*}\\\textsuperscript{1}Department of Psychological and Brain Sciences,\\Dartmouth College,
Hanover, NH\\[0.1cm]\textsuperscript{2}Carney Institute for Brain Sciences,\\Brown University,
Providence, RI\\[0.1cm] \textsuperscript{*}Address correspondence to
jeremy.r.manning@dartmouth.edu}

@@

\bibliographystyle{apacite}
\bibliography{CDL-bibliography/cdl}
